### 2018-03-20 papers.tex
Bump page numbers down globabally and adjust overrides

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\ainput{mftpc/trail-intro} % Before Stefan and Ben's paper
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{2cm}
	{}
\ainput{mftpc/itg-miss}

\addtrack
	{Cryptocurrencies}{\textit{A Dream}}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{Keywords: blockchain, P2P, digital currency}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{Keywords: communism, crypto-currency, CommieCoin}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\ainput{mftpc/coin-intro} % Before Rob's paper
\addpaper
	{That's Numberwangcoin!}
	{Robert J.\ Simmons}
	{Keywords: boredom, lost coins, shouty bits, speculative investment, the number 2 which you may remember from school is deadly to humans}
	{SIGBOVIK_2018_paper_27}
	{1cm}
	{}
\ainput{mftpc/pants-multi}
\ainput{mftpc/itg-wayoff}

@@

\addtrack
	{Ayyy Eye}{\textit{Afterimage of a Crimson Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}
	\addreview{SIGBOVIK_2018_review_28}{0cm}
\ainput{mftpc/coin-right}
\ainput{mftpc/itg-excellent}

>>>>

\addtrack
	{Theory}{\textit{Bottles}}
\addpaper
	{Sublinear colorings of 3-colorable graphs in linear time}
	{Thomas Tseng}
	{Keywords: graph coloring, approximation algorithms, analysis of algorithms}
	{SIGBOVIK_2018_paper_3}
	{0cm}
	{}
\addpaper
	{Cubic partitioning of simultaneous antipodal 4-corner-day time spaces}
	{R.\ Welch and G.\ Ray}
	{Keywords: timecube, conspiracy theories, applied mathematics, applied cubism, tuesdays, meridian time, word animals}
	{SIGBOVIK_2018_paper_2}
	{0cm}
	{}
\ainput{mftpc/trail-intro} % Before Stefan and Ben's paper
\addpaper
	{Construction of Eulerian trails in large graphs}
	{Stefan Muller and Ben Blum}
	{Keywords: walk, Eulerian trail, large graph}
	{SIGBOVIK_2018_paper_29}
	{0cm}
	{}
	\addreview{SIGBOVIK_2018_review_29}{0cm}
\edef\mainevensidemargin{\the\evensidemargin}
\setlength{\evensidemargin}{0pt}
\addpaper
	{Chess circuits}
	{Ross Dempsey, Sydney Timmerman, and Karl Osterbauer}
	{Keywords: chess, logic, boolean circuits}
	{SIGBOVIK_2018_paper_22}
	{3cm}
	{}
\setlength{\evensidemargin}{\mainevensidemargin}
\ainput{mftpc/itg-miss}

\addtrack
	{Cryptocurrencies}{\textit{A Dream}}
\addpaper
	{GradCoin:\ A poor-to-poor electronic cash transfer system}
	{Siddhant Jain}
	{Keywords: blockchain, P2P, digital currency}
	{SIGBOVIK_2018_paper_15}
	{0cm}
	{}
\addpaper
	{CommieCoin:\ Seizing the means of crypto-production}
	{Marx van Raasveldt \textit{et al.}}
	{Keywords: communism, crypto-currency, CommieCoin}
	{SIGBOVIK_2018_paper_11}
	{0cm}
	{}
\ainput{mftpc/coin-intro} % Before Rob's paper
\setlength{\evensidemargin}{0cm}
\addpaper
	{That's Numberwangcoin!}
	{Robert J.\ Simmons}
	{Keywords: boredom, lost coins, shouty bits, speculative investment, the number 2 which you may remember from school is deadly to humans}
	{SIGBOVIK_2018_paper_27}
	{2cm}
	{}
\setlength{\evensidemargin}{\mainevensidemargin}
\ainput{mftpc/pants-multi}
\ainput{mftpc/itg-wayoff}

@@

\addtrack
	{Ayyy Eye}{\textit{Afterimage of a Crimson Eye}}
\addpaper
	{PSYCHO:\ PerSonalitY CHaracterizatiOn of artificial intelligence}
	{Achal Dave and Rohit Girdhar}
	{Keywords: interpretability, psychology, deep learning, artificial intelligence, rorschach}
	{SIGBOVIK_2018_paper_8}
	{0cm}
	{}
\addpaper
	{The NUGGET non-linear piecewise activation}
	{Stephen Merity}
	{Keywords: deep learning, neural networks, nugget, nuggets, chicken nuggets, smart}
	{SIGBOVIK_2018_paper_10}
	{0cm}
	{}
\setlength{\evensidemargin}{0cm}
\addpaper
	{Substitute teacher networks:\ Learning with almost no supervision}
	{Samuel Albanie, James Thewlis, and Jo\~ao F.\ Henriques}
	{Keywords: substitute, teacher, networks}
	{SIGBOVIK_2018_paper_28}
	{1cm}
	{}
	\addreview{SIGBOVIK_2018_review_28}{0cm}
\setlength{\evensidemargin}{\mainevensidemargin}
\ainput{mftpc/coin-right}
\ainput{mftpc/itg-excellent}
